Appendix B

### 2020-03-31 contrast.Rmd
app b done

#### Meta
```{r meta, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(meta) #meta package current version effective March 2020

@@

#continuous data
m1 <- metacont(Ne, Me, Se, Nc, Mc, Sc, data = data, sm = "SMD")
summary(m1)
forest(m1, layout = "JAMA")
metabias(m1)
funnel(m1)
radial(m1)
```

@@

#fit model
#m2 <- rma(yi=SMD, vi=SMD_var, mods = ~study.ID, data = data)
m2 <- rma.uni(yi=SMD, vi=SMD_var, data = data, method = "REML") #restricted maximum-likelihood estimate
summary(m2)
plot(m2)

>>>>

### Meta
```{r meta, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(meta) #meta package current version effective March 2020

@@

#continuous data
m1 <- metacont(Ne, Me, Se, Nc, Mc, Sc, data = data, sm = "SMD")
summary(m1)

#viz
forest(m1, layout = "JAMA")
metabias(m1)
funnel(m1)
radial(m1)
```

@@

#fit model
#m2 <- rma(yi=SMD, vi=SMD_var, mods = ~study.ID, data = data)
m2 <- rma.uni(yi=SMD, vi=SMD_var, data = data, method = "REML") #restricted maximum-likelihood estimate
summary(m2)

#Viz
plot(m2)
```

\newpage
### Compiled contrasts
```{r contrasts, warning=FALSE, message=FALSE}
#compile random model outputs for contrast with metafor
estimate <- as_data_frame(m1$TE.random)
se <- as_data_frame(m1$seTE.random)
zval <- as_data_frame(m1$zval.random)
pval <- as_data_frame(m1$pval.random)
ci.lb <- as_data_frame(m1$lower.random)
ci.ub <- as_data_frame(m1$upper.random)
m1_tidy <- bind_cols(estimate, se, zval, pval, ci.lb, ci.ub) %>%
  rename(estimate = value, se = value1, zval = value2, pval = value3, ci.lb = value4, ci.ub = value5)

#compile output into table for contrast with meta
m2_tidy <- coef(summary(m2))
#m2_tidy

#compile key outputs
contrast_tidy <- bind_rows(m1_tidy, m2_tidy) %>%
  mutate(source = c("meta", "metafor")) %>%
  select(source, everything())

knitr::kable(contrast_tidy)
